---
title: ""
number-sections: true
format: 
  html:
    embed-resources: true
    code-tools: true
  pdf: default
editor_options: 
  chunk_output_type: console
execute:
  echo: true
  eval: true
  warning: false
  message: false
---

```{r}
library(tidyverse)
library(moderndive)
library(gapminder)
library(sjPlot)
library(stats)
library(jtools)
library(dplyr)
library(knitr)
library(janitor)
library(MASS)
library(caret)
```

# Data wrangling and subsetting

```{r}
#data wrangling and subseting
data = read.csv('dataset14.csv')
data <- na.omit(data)
mapping = c('Poor' = 0, 'Good' = 1)
data$Qualityclass = mapping[data$Qualityclass]
data$harvested = as.factor(data$harvested)
```

```{r}
#remove Cote d?Ivoire
data <- data %>% 
  filter(country_of_origin != "Cote d?Ivoire")
```

Here we map countriy_of_origin to corresponding continent

```{r}
unique(data$country_of_origin)
```

```{r}
continent_mapping <- c("China" = "Asia", "Mexico" = "North America", "Brazil" = "South America",
                       "Guatemala" = "North America", "Taiwan" = "Asia", "Uganda" = "Africa",
                       "Vietnam" = "Asia", "Thailand" = "Asia", "Colombia" = "South America",
                       "Kenya" = "Africa", "Costa Rica" = "North America", "Haiti" = "North America",
                       "Honduras" = "North America", "Philippines" = "Asia", "El Salvador" = "North America",
                       "Indonesia" = "Asia", "Ethiopia" = "Africa",
                       "Tanzania, United Republic Of" = "Africa", "Nicaragua" = "North America", "Malawi" = "Africa",
                       "United States" = "North America", "Peru" = "South America", "Rwanda" = "Africa",
                       "India" = "Asia", "Myanmar" = "Asia", "Papua New Guinea" = "Oceania", "Laos" = "Asia",
                       "Panama" = "North America", "Burundi" = "Africa",
                       "United States (Puerto Rico)" = "North America", "United States (Hawaii)" = "North America",
                       "Cote d'Ivoire" = "Africa", "Zambia" = "Africa", "Ecuador" = "South America")

# map countries to its continent
data$continent <- continent_mapping[data$country_of_origin]


```

```{r}
unique(data$continent)
```

# fitting GLM models

## Not removing variables

Here we have continent as our new categorical explanatory variable to fit a full logistic regression model:

```{r}
#Here we have continent as our new categorical explanatory variable
full_model = glm(Qualityclass ~ . - country_of_origin, family = binomial(link = 'logit'), data = data)
```

```{r}
summary(full_model)
```

It is shown that the 'harvested' and 'altitude_mean_meters' variables are insignificant. \## Using stepAIC to measure goodness of fit

```{r}
#direction = 'backward'
stepAIC(full_model)
```

```{r}
#direction = 'both'
stepAIC(full_model, direction = 'both')
```

Both indicated that to obtain a better glm model, 'harvested' and 'altitude_mean_meters' variable should be removed.\
\## Therefore we obtained a better glm model

```{r}
model1 = glm(formula = Qualityclass ~ aroma + flavor + acidity +
               category_two_defects + continent,
             family = binomial(link = "logit"), data = data)
summary(model1)
```
However, in the model with lowest AIC 525.88, variable category_two_defects is not so significant.

```{r}
model2 = glm(formula = Qualityclass ~ aroma + flavor + acidity +  
      continent, family = binomial(link = "logit"), data = data)
summary(model2)
```
The model dropping category_two_defects has AIC 526.97, which is slightly higher than 525.88. But all the variables is significant.

So we want to compare this two models by predictive power.

# predictive power

To compare predictive power of these two models, mean accuracy rate of 10-fold cross validation is used there.

```{r}
ctrl <- trainControl(method = "cv",
                     number = 10)
```
model including category_two_defects:
```{r}
set.seed(14)
model1.pred <- train(Qualityclass ~ aroma + flavor + 
                 acidity + category_two_defects + continent,
               data = data,
               method = "glm",
               family = "binomial",
               trControl = ctrl) 
accuracy1 = model1.pred$results$Accuracy
print(accuracy1)
```
model dropping category_two_defects:
```{r}
set.seed(14)
model2.pred <- train(Qualityclass ~ aroma + flavor + 
                 acidity + continent,
               data = data,
               method = "glm",
               family = "binomial",
               trControl = ctrl) 
accuracy2 = model2.pred$results$Accuracy
print(accuracy2)
```
Including variable category_two_defects cause a slightly higher accuracy rate.
test

# Conclusion

full_model: AIC=538.89, Residual deviance=502.89\
By removing 'harvested' and 'altitude_mean_meters' variable which were insignificant: AIC=525.9, Residual Deviance=507.9\

Finally, we choose the binomial generalized linear model with aroma, flavor, acidity, category_two_defects and continent to fit and predict quality class of coffee.
