---
title: "Factor affecting the quality of coffee beans"
number-sections: true
format: pdf
include-in-header: 
  text: |
    \usepackage{fvextra}
    \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
editor_options: 
  chunk_output_type: console
execute:
  echo: true
  eval: true
  warning: false
  message: false
---
Library packages. 

```{r}
library(tidyverse)
library(moderndive)
library(gapminder)
library(sjPlot)
library(stats)
library(jtools)
library(dplyr)
library(knitr)
library(janitor)
library(MASS)
library(caret)
library(GGally)
library(tables)
```

# Exploratory data analysis

Read data and convert Qualityclass and harvested year into categorical variables.
```{r}
data = read.csv('dataset14.csv')
data <- na.omit(data)
data$Qualityclass = as.factor(data$Qualityclass)
data$harvested = as.factor(data$harvested)
```

Deleting invalid observations there.
```{r}
#remove Cote d?Ivoire
data <- data %>% 
  filter(country_of_origin != "Cote d?Ivoire")
```

Here we map countriy_of_origin to corresponding continent.

```{r}
unique(data$country_of_origin)
```

```{r}
continent_mapping <- c("China" = "Asia", "Mexico" = "North America", "Brazil" = "South America",
                       "Guatemala" = "North America", "Taiwan" = "Asia", "Uganda" = "Africa",
                       "Vietnam" = "Asia", "Thailand" = "Asia", "Colombia" = "South America",
                       "Kenya" = "Africa", "Costa Rica" = "North America", "Haiti" = "North America",
                       "Honduras" = "North America", "Philippines" = "Asia", "El Salvador" = "North America",
                       "Indonesia" = "Asia", "Ethiopia" = "Africa",
                       "Tanzania, United Republic Of" = "Africa", "Nicaragua" = "North America", "Malawi" = "Africa",
                       "United States" = "North America", "Peru" = "South America", "Rwanda" = "Africa",
                       "India" = "Asia", "Myanmar" = "Asia", "Papua New Guinea" = "Oceania", "Laos" = "Asia",
                       "Panama" = "North America", "Burundi" = "Africa",
                       "United States (Puerto Rico)" = "North America", "United States (Hawaii)" = "North America",
                       "Cote d'Ivoire" = "Africa", "Zambia" = "Africa", "Ecuador" = "South America")

# map countries to its continent
data$continent <- continent_mapping[data$country_of_origin]
table(data$continent)

```

Delete sole observation in Oceania.

```{r}
data = data %>% filter(continent != 'Oceania')
```

Pairwise plot for variables:
```{r}
ggpairs(data[,-1],mapping = aes(color = Qualityclass))
```

Summary statistics for numerical variables with respect to different quality classes:
```{r}
table = tabular(aroma + flavor + acidity + category_two_defects + altitude_mean_meters ~ Qualityclass * (mean+sd+min+max+IQR), data=data)
print(table, type = 'latex')
```

Mapping good quality and poor quality into 1 and 0 respectively.
```{r}
data$Qualityclass = as.numeric(data$Qualityclass)
data$Qualityclass[data$Qualityclass == 2] = 0
```


# Model selection
Here we have continent as our new categorical explanatory variable to fit a full logistic regression model:

```{r}
#Here we have continent as our new categorical explanatory variable
full_model = glm(Qualityclass ~ . - country_of_origin, family = binomial(link = 'logit'), data = data)
```

```{r}
summary(full_model)
```

It is shown that the 'harvested' and 'altitude_mean_meters' variables are insignificant. 

Then we use stepAIC to measure goodness of fit.

```{r}
#direction = 'backward'
stepAIC(full_model)
```

Both indicated that to obtain a better glm model, 'harvested' and 'altitude_mean_meters' variable should be removed.

Therefore we obtained a better glm model.

```{r}
model1 = glm(formula = Qualityclass ~ aroma + flavor + acidity +
               category_two_defects + continent,
             family = binomial(link = "logit"), data = data)
summary(model1)
```

However, in the model with lowest AIC 523.88, variable category_two_defects is not so significant.

```{r}
model2 = glm(formula = Qualityclass ~ aroma + flavor + acidity +  
      continent, family = binomial(link = "logit"), data = data)
summary(model2)
```

The model dropping category_two_defects has AIC 524.97, which is slightly higher than 523.88. But all the variables are significant.

So we want to compare this two models by predictive power.

# Predictive power

To compare predictive power of these two models, mean accuracy rate of 10-fold cross validation is used there.

```{r}
set.seed(14)
folds <- createFolds(y=data$Qualityclass,k=10)
```

```{r}
total.n = 0
right1.n = 0
right2.n = 0
for(i in 1:10){
  fold.val = data[folds[[i]],]
  fold.train = data[-folds[[i]],]
  model1.val = glm(Qualityclass ~ aroma + flavor + acidity +
               category_two_defects + continent,
             family = binomial(link = "logit"), data = fold.train)
  predict1.val = ifelse(predict(model1.val, type='response',newdata=fold.val)>0.5, 1, 0)
  model2.val = glm(Qualityclass ~ aroma + flavor + acidity + continent,
             family = binomial(link = "logit"), data = fold.train)
  predict2.val = ifelse(predict(model2.val, type='response',newdata=fold.val)>0.5, 1, 0)
  total.n = total.n + nrow(fold.val)
  right1.n = right1.n + sum(predict1.val == fold.val$Qualityclass)
  right2.n = right2.n + sum(predict2.val == fold.val$Qualityclass)
}
cat('Mean accuracy rate for model including category_two_defects: ', right1.n/total.n, "\n",'Mean accuracy rate for model dropping category_two_defects: ', right2.n/total.n,"\n")

```

Including variable category_two_defects cause a slightly higher accuracy rate.

# Result and Conclusion

We start with full_model whose AIC=536.89, Residual deviance=502.89.\
By removing 'harvested' and 'altitude_mean_meters' variable which were insignificant: AIC=523.88, Residual Deviance=507.88.

Finally, we choose the binomial generalized linear model with aroma, flavor, acidity, category_two_defects and continent to fit and predict quality class of coffee.

# Visualization for model

Based on the model we choose, estimated probabilities for a good quality class with respect to each variable:

1. aroma

```{r}
plot_model(model1, type = "pred", terms = "aroma[all]")
```

The predicted probability of Qualityclass increases sharply as the aroma score increases. This suggests a strong positive association between the quality of coffee and its aroma.

2. flavor

```{r}
plot_model(model1, type = "pred", terms = "flavor[all]")
```

Similar to aroma, the probability of a higher Qualityclass increases sharply with the flavor score. Flavor appears to be a significant predictor of coffee quality.

3. acidity

```{r}
plot_model(model1, type = "pred", terms = "acidity[all]")
```

The plot shows that higher acidity scores are associated with a higher probability of Qualityclass. There is a positive relationship between acidity and coffee quality, though it seems to have a threshold effect, with probability rising more sharply after a certain point.

4. category_two_defects

```{r}
plot_model(model1, type = "pred", terms = "category_two_defects[all]")
```

As the number of defects increases, the probability of a higher Qualityclass increases. This is somewhat counterintuitive, as one might expect more defects to decrease quality. However, the confidence band is wide, suggesting there may be high variability or that this variable interacts with others in complex ways.

5. continent

```{r}
plot_model(model1, type = "pred", terms = "continent")
```
There appears to be variation among continents, with some showing higher probabilities than others, suggesting geographical variation in coffee quality.
